\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
  \item\small{
    {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeScholarshipHeading}[2]{
  \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge \scshape Joey Shi} \\ \vspace{1pt}
  \small
  \href{https://joeyshi.xyz}{\underline{joeyshi.xyz}} ~
  \href{mailto:root@joeyshi.xyz}{\underline{root@joeyshi.xyz}} ~
  \href{https://linkedin.com/in/joeyshi12/}{\underline{linkedin.com/in/joeyshi12}} ~
  \href{https://github.com/joeyshi12}{\underline{github.com/joeyshi12}}
  \vspace{-4pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amazon}{May 2025 -- Present}
      {Software Development Engineer}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{On a team building developer tools and AI agents used by engineers across Amazon.}
        \resumeItem{Re-architected an internal Slack knowledge gateway from sync to async with a dispatcher Lambda and SQS, cutting acknowledgement latency to ~0.5s and eliminating timeout errors.}
        \resumeItem{Scaled an internal diagnostic CLI into a team-wide operations platform with multi-service/region config, SSH log fetching, CloudWatch alarm integration, and stuck-thread detection.}
        \resumeItem{Integrated enterprise SSO into an internal API across beta, gamma, and prod using AWS CDK, and authored the SOP teammates use to add auth to their endpoints.}
      \resumeItemListEnd

    \resumeSubheading
      {Visier Inc.}{April 2023 -- May 2025}
      {Software Developer II}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{On the data ingestion team for an HR analytics SaaS platform, implemented and owned Scala data connectors for MySQL, BambooHR, Oracle Fusion, Medallia, Greenhouse, Redshift, and Snowflake; rapid delivery of the MySQL connector unblocked a new customer contract.}
        \resumeItem{Added limit/offset pagination to the MySQL connector, fixing gateway timeouts on customers with very large source tables.}
        \resumeItem{Built data flow graph visualization libraries in TypeScript and Angular to simplify ETL pipeline configuration.}
        \resumeItem{Owned the on-call rotation for all connectors I shipped, resolving customer-impacting ingestion failures in production.}
      \resumeItemListEnd

    \resumeSubheading
      {Vital Mechanics Research}{May 2022 -- Oct 2022}
      {Software Developer}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{At a research lab building 3D clothing simulation software, developed a Python CLI tool for extracting garment geometry and stitch information from glTF and DXF files.}
        \resumeItem{Implemented mathematical optimization algorithms to model garment edges as B\'ezier curves and approximate stitch point positions along the garment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
  \vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\href{https://karet.joeyshi.xyz/}{\textbf{Karet Analytics Platform}} $|$ \emph{Rust \textperiodcentered{} Axum \textperiodcentered{} Polars \textperiodcentered{} Next.js \textperiodcentered{} React \textperiodcentered{} S3 \textperiodcentered{} Docker}}{}
      \resumeItemListStart
        \resumeItem{Built an open-source analytics platform from three services: a Next.js/React UI, a stateless data processing server, and an S3-compatible object store, persisting all state as objects in S3.}
        \resumeItem{Engineered a JSON-AST expression language evaluated row-by-row to ingest CSVs into Parquet partitioned by year and month, with dashboard panels, layouts, and aggregations defined entirely as JSON config.}
        \resumeItem{Wired S3 upload events to a debounced, idempotent runner so new files auto-trigger ETL jobs, and secured single-admin login with scrypt hashing.}
      \resumeItemListEnd
      \vspace{-13pt}
    \resumeProjectHeading
      {\href{https://github.com/joeyshi12/diff-eq-solver}{\textbf{Differential Equation Solver}} $|$ \emph{Python \textperiodcentered{} Matplotlib \textperiodcentered{} Tkinter}}{}
      \resumeItemListStart
        \resumeItem{Implemented finite difference algorithms to solve ordinary and partial differential equations, with a Tkinter GUI and animated Matplotlib plots for visualizing solutions.}
        \resumeItem{Built a CI/CD pipeline with PyTest, Tox, and GitHub Actions, and published the application on the Python Package Index.}
      \resumeItemListEnd
      \vspace{-13pt}
    \resumeProjectHeading
      {\href{https://devtools.joeyshi.xyz/}{\textbf{Developer Tools Suite}} $|$ \emph{Python \textperiodcentered{} Flask \textperiodcentered{} TypeScript \textperiodcentered{} Docker \textperiodcentered{} Caddy}}{}
      \resumeItemListStart
        \resumeItem{Built and self-host a suite of web-based developer tools behind a Caddy reverse proxy, including a webhook request inspector and a DNS resolver that traces iterative queries from the root servers down the nameserver hierarchy.}
        \resumeItem{Designed PQL, a SQL-like query language with an EBNF grammar and recursive-descent parser that compiles tabular data into 2D plots, and a JSON-to-data-model transpiler targeting Python, TypeScript, Java, Scala, and Proto3; published both to npm and PyPI.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia}{Sep 2018 -- May 2023}
      {Bachelor of Science $|$ Combined Major in Computer Science and Mathematics, with Distinction}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Graduated with a 4.0/4.0 GPA.}
        \resumeItem{Received the Stanley M. Grant Scholarship in Mathematics (2021) and Trek Excellence Scholarship (2020).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Python \textperiodcentered{} Rust \textperiodcentered{} Scala \textperiodcentered{} Java \textperiodcentered{} TypeScript \textperiodcentered{} JavaScript \textperiodcentered{} Proto3 \textperiodcentered{} HTML5 \textperiodcentered{} CSS3 \textperiodcentered{} C/C++ \textperiodcentered{} SQL \textperiodcentered{} Zsh} \\
      \textbf{Frameworks/Libraries}{: Angular \textperiodcentered{} React \textperiodcentered{} Next.js \textperiodcentered{} Node.js \textperiodcentered{} Axum \textperiodcentered{} D3.js \textperiodcentered{} Flask \textperiodcentered{} Pandas \textperiodcentered{} Polars \textperiodcentered{} Pytest \textperiodcentered{} AWS CDK} \\
      \textbf{Tools/Technologies}{: S3 \textperiodcentered{} Lambda \textperiodcentered{} SQS \textperiodcentered{} DynamoDB \textperiodcentered{} CloudWatch \textperiodcentered{} Parquet \textperiodcentered{} Docker \textperiodcentered{} Git \textperiodcentered{} Arch Linux \textperiodcentered{} Neovim} \\
    }}
  \end{itemize}

\end{document}
